Variations on a Bayesian Theme: Comparing Bayesian Models of Referential Reasoning

### 2013-10-28 main.tex
revised abstract

% ======= Packages ======

%    ### General ###
%\usepackage{latexsym}
\usepackage{enumerate}

@@

%\usepackage{lgcommands}
\usepackage{tikz,subfigure}
   \usetikzlibrary{shapes.geometric}

%    ### Linguistics ###
%\usepackage{tipa}   % International Phonetic Alphabet

@@

\begin{abstract}
Recent developments in Bayesian experimental pragmatics have received much attention, as it provides us with a quantitative model formalizing core concepts in traditional pragmatic theories and the predictions it makes fit empirical data nicely. Despite its theoretical advantage and empirical success, there are still several conceptual issues in the Bayesian Rational Speech Act (RSA) model that need further clarification. In this paper, we analyze a few design choices made in RSA that have intuitively equally plausible alternatives motivated from related game-theoretic approaches to pragmatics, and compare the original RSA model with these alternatives to empirical data. The result suggests that while RSA is better than most other variations, there is still room for improvement.
\end{abstract}

>>>>

% ======= Packages ======
\usepackage{etex}
%    ### General ###
%\usepackage{latexsym}
\usepackage{enumerate}

@@

%\usepackage{lgcommands}
\usepackage{tikz,subfigure}
   \usetikzlibrary{shapes.geometric}
\usepackage{pgfplots}
%    ### Linguistics ###
%\usepackage{tipa}   % International Phonetic Alphabet

@@

\begin{abstract}
Recent developments in Bayesian experimental pragmatics have received much attention. The Rational Speech Act (RSA) model formalizes core concepts in traditional pragmatic theories quantitatively and makes predictions that fit empirical data nicely. In this paper, we analyze the RSA model and its relation to the closely related game-theoretic approaches to pragmatics, by spelling out its \emph{belief}, \emph{goal} and \emph{action} components. We introduce some alternatives motivated from the game-theoretic models and compare them with the RSA model to new experimental data. The result suggests that the RSA model could be adapted and extended to improve its predictive power.

\end{abstract}
